Scalable Clustering of Genotype Information using MapReduce

### 2014-05-17 doc/publications/incob2014/paper.tex
Some changes

\newcommand{\OneReal}{OneChr\_1K}
\newcommand{\SixReal}{SixChr\_1K}
\newcommand{\FullReal}{Full\_1K}
\newcommand{\SixArtiExact}{SixChr\_10K\_0}
\newcommand{\SixArtiNoise}{SixChr\_100K\_10}

@@

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
\begin{table}[h!]
\caption{Datasets used in this study.}
      \begin{tabular}{lrrrrr}
        \hline
           & individuals  & variants  & population & families & noise\\ 
           & & &groups&& \\ \hline
        \OneReal & 1,092 & 816,115  & 4 & 855 & NA\\
        \SixReal & 1,092 & 15,161,339 & 4 & 855 & NA\\
        \FullReal\ & 1,092 & 38,219,238 & 4 & 855 & NA\\
	\SixArtiExact\ & 10,920 & 15,161,339 & 4 & 855 & 0 \\ 
	\SixArtiNoise\ & 10,920 & 15,161,339 & 4 & 855 & 10 \\ 
      \end{tabular}
      \label{datasets}
\end{table}

\begin{table}[h!]
\caption{Adjusted Rand index (accuracy).}
      \begin{tabular}{lcccc}
        \hline
           & \chrOnePop & \FullPop  & hapmap \\ \hline
        Mahout, k=4 & 0.664 & ..&..\\
        Mahout, k=10 & 0.714 & ..&..\\
        Mahout, k=20 & 0.769 & .. & ..\\ 
        Mahout, k=30 & 0.728 & .. & ..\\ 
        R, k=4 & .. & - & -\\
        R, k=10 & .. & - & -\\
        R, k=20 & .. & - & -\\ 
        R, k=30 & .. & - & -\\ \hline
      \end{tabular}
      \label{datasetsAcc}
\end{table}

\begin{table}[h!]
\caption{Resources consumed.}
      \begin{tabular}{lccccc}
      \hline
      &&\multicolumn{2}{ c }{Memory (kb)}&\multicolumn{2}{ c }{Time (s)} \\
        \hline
           & Nodes & pmem & vmem  & pre-processing & clustering \\ \hline
        R, \chrOnePop & 1 & 17696940 & 18000196 &3341 & 7\\
        Mahout,\chrOnePop & 1 & 1831160 & 7646232 & 1255 & 594\\
        Mahout, \FullPop & .. &.. & .. & ..&..\\ 
        Mahout, 4 nodes & .. & .. & .. & ..&..\\ 
        \hline
      \end{tabular}
      \label{datasetsTime}
\end{table}

>>>>

\newcommand{\OneReal}{OneChr\_1K}
\newcommand{\SixReal}{SixChr\_1K}
\newcommand{\FullReal}{Full\_1K}
\newcommand{\SixArtiExact}{Chr19\_5K\_0}
\newcommand{\SixArtiNoise}{Chr19\_5K\_10}

@@

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
\begin{table}[h!]
\caption{Datasets used in this study.}
      \begin{tabular}{lrrrrr}
        \hline
           & individuals  & variants  & population & families & noise\\ 
           & & &groups&& \\ \hline
        \OneReal & 1,092 & 816,115  & 4 & 855 & NA\\
        \SixReal & 1,092 & 15,161,339 & 4 & 855 & NA\\
        \FullReal\ & 1,092 & 38,219,238 & 4 & 855 & NA\\
	\SixArtiExact\ & 5,460 & 816,115 & 4 & 855 & 0 \\ 
	\SixArtiNoise\ & 5,460 & 816,115 & 4 & 855 & 10 \\ 
      \end{tabular}
      \label{datasets}
\end{table}

\begin{table}[h!]
\caption{Adjusted Rand index (accuracy).}
      \begin{tabular}{lcc}
        \hline
           & \chrOnePop & \FullPop   \\ \hline
        Mahout, k=4 & 0.664\\
        Mahout, k=10 & 0.714 \\
        Mahout, k=20 & 0.769 \\ 
        Mahout, k=30 & 0.728  \\ 
        R, k=4 & .. & - \\
        R, k=10 & .. & - \\
        R, k=20 & .. & - \\ 
        R, k=30 & .. & - \\ \hline
      \end{tabular}
      \label{datasetsAcc}
\end{table}

\begin{table}[h!]
\caption{Resources consumed.}
      \begin{tabular}{lccccc}
      \hline
      &&\multicolumn{2}{ c }{Memory (kb)}&\multicolumn{2}{ c }{Time (s)} \\
        \hline
           & Nodes & pmem & vmem  & pre-processing & clustering \\ \hline
        R, \chrOnePop & 1 & 17,696,940 & 18,000,196 &3,341 & 7\\
        Mahout,\chrOnePop & 1 & 1,831,160 & 7646232 & 1,255 & 594\\
        Mahout, \SixReal & 1 & 13,036,836 & 36,542,380 & 19,500 &..\\ 
        Mahout, \SixArtiExact & 1 & 5,804,660 & 39,075,548 & 2,024 & ..\\ 
        \hline
      \end{tabular}
      \label{datasetsTime}
\end{table}
